---
title: "modelos_multinivel"
author: "Anais Herrera Leighton"
date: "29-11-2021"
output:
  pdf_document:
    toc: no
  bookdown::pdf_document2:
    template: null
    keep_tex: no
    number_sections: no
    toc: no
  html_document:
    toc: yes
    code_folding: hide
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{times}
- \usepackage{caption}
- \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
- \usepackage{graphicx}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
geometry: margin=0.78in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	error = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r, include=FALSE}
pacman::p_load(haven,dplyr)
```

# Síntesis de resultados
```{r, include=FALSE}
load(file= "../input/data/proc/2009/data_chl.Rdata")
data2009_chl=data2009_chl0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2009/data_col.Rdata")
data2009_col=data2009_col0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2009/data_dom.Rdata")
data2009_dom=data2009_dom0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2009/data_mex.Rdata")
data2009_mex=data2009_mex0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_chl.Rdata")
data2016_chl=data2016_chl0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_col.Rdata")
data2016_col=data2016_col0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_dom.Rdata")
data2016_dom=data2016_dom0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_mex.Rdata")
data2016_mex=data2016_mex0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()
```

```{r, echo=FALSE, results='asis'}
pacman::p_load(summarytools,haven,sjPlot,dplyr,lme4,haven,texreg,knitr,kableExtra,bda,lmerTest)

data2009 <- rbind(data2009_chl,data2009_col,data2009_dom,data2009_mex)
data2009$IDSCHOOL2<- as.numeric(data2009$IDCNTRY*100000 + data2009$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2009$IDCNTRY2 <- ifelse((data2009$IDCNTRY==152), 1, # Chile
                   ifelse((data2009$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2009$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2009$IDCNTRY==484), 4, NA)))) # Mexico

reg_legal <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2009)
reg_illegal <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2009)
reg_elect <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2009)

#          "Students' expected participation in future legal protest",
#          "Students' expected participation in future illegal protest",
#          "Students' expected adult electoral participation"

caption <- "Students' expected... (ICCS 2009)"
knitreg(list(reg_legal,reg_illegal,reg_elect), 
        custom.model.names = c(
          "participation in future legal protest",
          "participation in future illegal protest",
          "adult electoral participation"
        ), 
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico",
                              "Intercepto",
                              "ISCED level 4, 5A, 5B or 6 (Ref. Level 3 or less)",
                              "More than 100 books (Ref. 0-100 books)",
                              "Attitudes towards disobeying the law",
                              "Attitudes towards the use of violence",
                              "Citizenship self-efficacy",
                              "Civic participation at school (student)",
                              "Civic participation at school (school)",
                              "Civic knowledge"),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )

```


```{r, echo=FALSE, results='asis'}
data2016 <- rbind(data2016_chl,data2016_col,data2016_dom,data2016_mex)
data2016$IDSCHOOL2<- as.numeric(data2016$IDCNTRY*100000 + data2016$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2016$IDCNTRY2 <- ifelse((data2016$IDCNTRY==152), 1, # Chile
                   ifelse((data2016$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2016$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2016$IDCNTRY==484), 4, NA)))) # Mexico

reg_legal <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV+ (1 | IDSCHOOL2), data=data2016)
reg_illegal <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2016)
reg_elect <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2016)

caption <- "Students' expected... (ICCS 2016)"
knitreg(list(reg_legal,reg_illegal,reg_elect), 
        custom.model.names = c(
          "participation in future legal protest",
          "participation in future illegal protest",
          "adult electoral participation"
        ), 
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico",
                              "Intercepto",
                              "ISCED level 4, 5A, 5B or 6 (Ref. Level 3 or less)",
                              "More than 100 books (Ref. 0-100 books)",
                              "Attitudes towards disobeying the law",
                              "Attitudes towards the use of violence",
                              "Citizenship self-efficacy",
                              "Civic participation at school (student)",
                              "Civic participation at school (school)",
                              "Civic knowledge"),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )

```

\newpage

# Datos 2009
```{r, include=FALSE}
load(file= "../input/data/proc/2009/data_chl.Rdata")
data2009_chl=data2009_chl0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

# data2009_chl2=data2009_chl0 %>% dplyr::select(HISCED2, HOMELIT2, HISEI, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, HISCED2, HOMELIT2, DISLAW_rec, ATTVIOL_rec, PARTSCHL_rec, IDSCHOOL=IDSCHOOL.x) %>% as.data.frame() %>%  na.omit() # bbdd con variable de estatus ocupacional, disminuye el n y no se mide de la misma manera en las dos olas (en iccs 2009 solo se pregunta por la ocupación y en iccs 2016 se pregunta además por las actividades que hace). Esta es la variable: HISEI

load(file= "../input/data/proc/2009/data_col.Rdata")
data2009_col=data2009_col0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2009/data_dom.Rdata")
data2009_dom=data2009_dom0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2009/data_mex.Rdata")
data2009_mex=data2009_mex0 %>% dplyr::select(HISCED2, HOMELIT2, LEGPROT_rec, ILLPROT_rec, ELECPART_rec, DISLAW_rec, ATTVIOL_rec, CITEFF_rec, PARTSCHL_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()
```

```{r, include=FALSE}
#################################
#### Variables dependientes ####
#################################

# Variable Name: LEGPROT 
# Description: Students' expected participation in future legal protest
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally weighted countries
# Source: 
#IS2P31A Writing a letter to a newspaper
#IS2P31B Wearing a badge or t-shirt expressing your opinion
#IS2P31C Contacting an <elected representative>
#IS2P31D Taking part in a peaceful march or rally
#IS2P31E Collecting signatures for a petition
#IS2P31F Choosing not to buy certain products

# Variable Name: ILLPROT 
# Description: Students' expected participation in future illegal protest
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally  weighted countries
# Source: 
#IS2P31G Spray-painting protest slogans on walls
#IS2P31H Blocking traffic
#IS2P31I Occupying public buildings

# Variable Name: ELECPART 
# Description: Students' expected adult electoral participation
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally  weighted countries
# Source: 
#IS2P32A Vote in <local elections>
#IS2P32B Vote in <national elections>
#IS2P32C Get information about candidates before voting in an election

##################################
#### Variables independientes ####
##################################

# HISCED2 # Educación

# HOMELIT2 # Cantidad de libros en el hogar

# Variable Name: DISLAW
# Description: Student attitudes towards disobeying the law
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally weighted countries
# Pregunta: ¿En qué medida está de acuerdo o en desacuerdo con las siguientes declaraciones sobre situaciones en las que se desobedece la ley?
# Se puede desobedecer una ley ...
# Source: 
#LS2P05A when it is the only alternative left for achieving important objectives.
#LS2P05B when it is the only way one has to help one's family.
#LS2P05C when others who disobeyed it were not punished.
#LS2P05D when others do it.
#LS2P05E when one distrusts the enacting body.
#LS2P05F when one is sure nobody will realize.
#LS2P05H when nobody gets hurt.
#LS2P05I when it is not done with bad intentions.
#LS2P05J when one is not familiar with the law. (no se repite)
#LS2P05K when one distrusts the authority executing the law. (no se repite) 
#LS2P05L when one can obtain economic benefits. 

# Variable Name: ATTVIOL
# Description: Student attitudes towards the use of violence
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally weighted countries
# Source: 
#LS2P08A He who does me harm will have to pay for it.
#LS2P08B Watching fights between classmates is fun.
#LS2P08C If you cannot do it the easy way, do it the hard way.
#LS2P08D You have to fight so people do not think you are a coward.

# Variable  Name: CITEFF
# Description: Students' citizenship self-efficacy
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally weighted countries
# Source: 
#IS2P30A Discuss a newspaper article about a conflict between countries
#IS2P30B Argue your point of view about a controversial political or social issue
#IS2P30C Stand as a candidate in a <school election>
#IS2P30D Organise a group of students in order to achieve changes at school
#IS2P30E Follow a television debate about a controversial issue
#IS2P30F Write a letter to a newspaper giving your view on a current issue
#IS2P30G Speak in front of your class about a social or political issue

#Variable Name: INTPOLS
#Description: Students' Interest in politics and social issues
#Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally weighted countries
#Source: 
#IS2P22A Political issues within your <local community>
#IS2P22B Political issues in your country
#IS2P22C Social issues in your country
#IS2P22D Politics in other countries
#IS2P22E International politics

# Variable Name: PARTSCHL
# Description: Students' civic participation at school
# Procedure: IRT WLE scores with mean of 50 and standard deviation of 10 for equally weighted countries
# Source: 
#IS2G15A Voluntary participation in school-based music or drama activities outside of regular lessons (no se repite)
#IS2G15B Active participation in a debate
#IS2G15C Voting for <class representative> or <school parliament>
#IS2G15D Taking part in decision-making about how the school is run
#IS2G15E Taking part in discussions at a <student assembly>
#IS2G15F Becoming a candidate for <class representative> or <school parliament> (no se repite)
```

# Modelos de regresión multinivel: 2009
```{r, include=FALSE}
pacman::p_load(summarytools,haven,sjPlot,dplyr,lme4,haven,texreg,knitr,kableExtra,bda,lmerTest)

coef_names <- c(
          "Intercepto",
          "ISCED level 4, 5A, 5B or 6 (Ref. Level 3 or less)",
          "More than 100 books (Ref. 0-100 books)",
          "Attitudes towards disobeying the law",
          "Attitudes towards the use of violence",
          "Citizenship self-efficacy",
          "Civic participation at school (student)",
          "Civic participation at school (school)",
          "Civic knowledge"
          )

#coef_names <- c(
#          "Intercepto",
#          "ISCED level 2 (Ref. Not complete level 2)",
#          "ISCED level 3",
#          "ISCED level 4, 5A, 5B or 6",
#          "11-25 books (Ref. 0-10 books)",
#          "26-100 books",
#          "101-200 books",
#          "More than 200 books",
#          "Attitudes towards disobeying the law",
#          "Attitudes towards the use of violence",
#          "Citizenship self-efficacy",
#          "Civic participation at school (student)",
#          "Civic participation at school (school)",
#          "Civic knowledge"
#          )

#omit_coef <- "(PV1CIV)"
#footnote<- "\\item %stars. \\item Todos los modelos son controlados por la región de residencia (p>0.05), la dependencia administrativa de la escuela (p>0.05) y el nivel de conocimiento cívico del estudiante ($p$<0.05)"
scale_box <- 0.825
```

## Participación política en actividades legales

### Chile
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_chl)
reg2 <- lmer(LEGPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_chl)
reg3 <- lmer(LEGPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_chl)
reg4 <- lmer(LEGPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_chl)
reg5 <- lmer(LEGPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_chl)
reg6 <- lmer(LEGPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_chl)
reg7 <- lmer(LEGPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_chl)
reg8 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_chl)

caption <- "Students' expected participation in future legal protest (Chile 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Colombia
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_col)
reg2 <- lmer(LEGPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_col)
reg3 <- lmer(LEGPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_col)
reg4 <- lmer(LEGPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_col)
reg5 <- lmer(LEGPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_col)
reg6 <- lmer(LEGPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_col)
reg7 <- lmer(LEGPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_col)
reg8 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_col)

caption <- "Students' expected participation in future legal protest (Colombia 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### República Dominicana
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_dom)
reg2 <- lmer(LEGPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_dom)
reg3 <- lmer(LEGPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_dom)
reg4 <- lmer(LEGPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_dom)
reg5 <- lmer(LEGPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_dom)
reg6 <- lmer(LEGPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_dom)
reg7 <- lmer(LEGPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_dom)
reg8 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_dom)

caption <- "Students' expected participation in future legal protest (Dominican Republic 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### México
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_mex)
reg2 <- lmer(LEGPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_mex)
reg3 <- lmer(LEGPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_mex)
reg4 <- lmer(LEGPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_mex)
reg5 <- lmer(LEGPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_mex)
reg6 <- lmer(LEGPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_mex)
reg7 <- lmer(LEGPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_mex)
reg8 <- lmer(LEGPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_mex)

caption <- "Students' expected participation in future legal protest (Mexico 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Todos los países
```{r, echo=FALSE, results='asis'}
data2009 <- rbind(data2009_chl,data2009_col,data2009_dom,data2009_mex)
data2009$IDSCHOOL2<- as.numeric(data2009$IDCNTRY*100000 + data2009$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2009$IDCNTRY2 <- ifelse((data2009$IDCNTRY==152), 1, # Chile
                   ifelse((data2009$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2009$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2009$IDCNTRY==484), 4, NA)))) # Mexico

reg1 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + (1 | IDSCHOOL2), data=data2009)
reg2 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + (1 | IDSCHOOL2), data=data2009)
reg3 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HOMELIT2) + (1 | IDSCHOOL2), data=data2009)
reg4 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + DISLAW_rec + (1 | IDSCHOOL2), data=data2009)
reg5 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + ATTVIOL_rec + (1 | IDSCHOOL2), data=data2009)
reg6 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + CITEFF_rec + (1 | IDSCHOOL2), data=data2009)
reg7 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL2), data=data2009)
reg8 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + PV1CIV + (1 | IDSCHOOL2), data=data2009)
reg9 <- lmer(LEGPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2009)

caption <- "Students' expected participation in future legal protest (2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8,reg9),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico", 
                              coef_names),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

## Participación política en actividades ilegales

### Chile
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_chl)
reg2 <- lmer(ILLPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_chl)
reg3 <- lmer(ILLPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_chl)
reg4 <- lmer(ILLPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_chl)
reg5 <- lmer(ILLPROT_rec ~ 1 + CITEFF_rec  + (1 | IDSCHOOL), data=data2009_chl)
reg6 <- lmer(ILLPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_chl)
reg7 <- lmer(ILLPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_chl)
reg8 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_chl)

caption <- "Students' expected participation in future illegal protest (Chile 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Colombia
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_col)
reg2 <- lmer(ILLPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_col)
reg3 <- lmer(ILLPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_col)
reg4 <- lmer(ILLPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_col)
reg5 <- lmer(ILLPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_col)
reg6 <- lmer(ILLPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_col)
reg7 <- lmer(ILLPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_col)
reg8 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_col)

caption <- "Students' expected participation in future illegal protest (Colombia 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### República Dominicana
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_dom)
reg2 <- lmer(ILLPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_dom)
reg3 <- lmer(ILLPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_dom)
reg4 <- lmer(ILLPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_dom)
reg5 <- lmer(ILLPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_dom)
reg6 <- lmer(ILLPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_dom)
reg7 <- lmer(ILLPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_dom)
reg8 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_dom)

caption <- "Students' expected participation in future illegal protest (Dominican Republic 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### México
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_mex)
reg2 <- lmer(ILLPROT_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_mex)
reg3 <- lmer(ILLPROT_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_mex)
reg4 <- lmer(ILLPROT_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_mex)
reg5 <- lmer(ILLPROT_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_mex)
reg6 <- lmer(ILLPROT_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_mex)
reg7 <- lmer(ILLPROT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_mex)
reg8 <- lmer(ILLPROT_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_mex)

caption <- "Students' expected participation in future illegal protest (Mexico 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Todos los países
```{r, echo=FALSE, results='asis'}
data2009 <- rbind(data2009_chl,data2009_col,data2009_dom,data2009_mex)
data2009$IDSCHOOL2<- as.numeric(data2009$IDCNTRY*100000 + data2009$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2009$IDCNTRY2 <- ifelse((data2009$IDCNTRY==152), 1, # Chile
                   ifelse((data2009$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2009$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2009$IDCNTRY==484), 4, NA)))) # Mexico

reg1 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + (1 | IDSCHOOL2), data=data2009)
reg2 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + (1 | IDSCHOOL2), data=data2009)
reg3 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HOMELIT2) + (1 | IDSCHOOL2), data=data2009)
reg4 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + DISLAW_rec + (1 | IDSCHOOL2), data=data2009)
reg5 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + ATTVIOL_rec + (1 | IDSCHOOL2), data=data2009)
reg6 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + CITEFF_rec + (1 | IDSCHOOL2), data=data2009)
reg7 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL2), data=data2009)
reg8 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + PV1CIV + (1 | IDSCHOOL2), data=data2009)
reg9 <- lmer(ILLPROT_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2009)

caption <- "Students' expected participation in future illegal protest (2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8,reg9),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico", coef_names),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

## Participación política formal

### Chile
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_chl)
reg2 <- lmer(ELECPART_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_chl)
reg3 <- lmer(ELECPART_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_chl)
reg4 <- lmer(ELECPART_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_chl)
reg5 <- lmer(ELECPART_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_chl)
reg6 <- lmer(ELECPART_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_chl)
reg7 <- lmer(ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_chl)
reg8 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_chl)

caption <- "Students' expected adult electoral participation (Chile 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Colombia
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_col)
reg2 <- lmer(ELECPART_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_col)
reg3 <- lmer(ELECPART_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_col)
reg4 <- lmer(ELECPART_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_col)
reg5 <- lmer(ELECPART_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_col)
reg6 <- lmer(ELECPART_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_col)
reg7 <- lmer(ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_col)
reg8 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_col)

caption <- "Students' expected adult electoral participation (Colombia 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### República Dominicana
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_dom)
reg2 <- lmer(ELECPART_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_dom)
reg3 <- lmer(ELECPART_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_dom)
reg4 <- lmer(ELECPART_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_dom)
reg5 <- lmer(ELECPART_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_dom)
reg6 <- lmer(ELECPART_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_dom)
reg7 <- lmer(ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_dom)
reg8 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_dom)

caption <- "Students' expected adult electoral participation (Dominican Republic 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### México
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + (1 | IDSCHOOL), data=data2009_mex)
reg2 <- lmer(ELECPART_rec ~ 1 + factor(HOMELIT2) + (1 | IDSCHOOL), data=data2009_mex)
reg3 <- lmer(ELECPART_rec ~ 1 + DISLAW_rec + (1 | IDSCHOOL), data=data2009_mex)
reg4 <- lmer(ELECPART_rec ~ 1 + ATTVIOL_rec + (1 | IDSCHOOL), data=data2009_mex)
reg5 <- lmer(ELECPART_rec ~ 1 + CITEFF_rec + (1 | IDSCHOOL), data=data2009_mex)
reg6 <- lmer(ELECPART_rec ~ 1 + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL), data=data2009_mex)
reg7 <- lmer(ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2009_mex)
reg8 <- lmer(ELECPART_rec ~ 1 + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2009_mex)

caption <- "Students' expected adult electoral participation (Mexico 2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Todos los países
```{r, echo=FALSE, results='asis'}
data2009 <- rbind(data2009_chl,data2009_col,data2009_dom,data2009_mex)
data2009$IDSCHOOL2<- as.numeric(data2009$IDCNTRY*100000 + data2009$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2009$IDCNTRY2 <- ifelse((data2009$IDCNTRY==152), 1, # Chile
                   ifelse((data2009$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2009$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2009$IDCNTRY==484), 4, NA)))) # Mexico

reg1 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + (1 | IDSCHOOL2), data=data2009)
reg2 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + (1 | IDSCHOOL2), data=data2009)
reg3 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(HOMELIT2) + (1 | IDSCHOOL2), data=data2009)
reg4 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + DISLAW_rec + (1 | IDSCHOOL2), data=data2009)
reg5 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + ATTVIOL_rec + (1 | IDSCHOOL2), data=data2009)
reg6 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + CITEFF_rec + (1 | IDSCHOOL2), data=data2009)
reg7 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + PARTSCHL_rec + mean_op_esc + (1 | IDSCHOOL2), data=data2009)
reg8 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + PV1CIV + (1 | IDSCHOOL2), data=data2009)
reg9 <- lmer(ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(HISCED2) + factor(HOMELIT2) + DISLAW_rec + ATTVIOL_rec + CITEFF_rec + PARTSCHL_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2009)

caption <- "Students' expected adult electoral participation (2009)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8,reg9),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico", coef_names),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

# Datos 2016
```{r, include=FALSE}
load(file= "../input/data/proc/2016/data_chl.Rdata")
data2016_chl=data2016_chl0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_col.Rdata")
data2016_col=data2016_col0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_dom.Rdata")
data2016_dom=data2016_dom0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()

load(file= "../input/data/proc/2016/data_mex.Rdata")
data2016_mex=data2016_mex0 %>% dplyr::select(S_HISCED2, S_HOMLIT2, S_LEGACT_rec, S_ILLACT_rec, S_ELECPART_rec, L_DISLAW_rec, L_ATTVIOL_rec, S_SCHPART_rec, S_CITEFF_rec, mean_op_esc, PV1CIV, IDSCHOOL=IDSCHOOL.x, IDCNTRY) %>% as.data.frame() %>%  na.omit()
```

```{r, include=FALSE}
#################################
#### Variables dependientes ####
#################################
# Variable Name: S_LEGACT_rec 
# Description: Students' expected participation in legal activities
# Procedure: IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation: Higher values indicating higher levels of expected engagement
# Trend Status: Not equated to ICCS 2009 given changes in stem and wording, new scale for ICCS 2016 (with similar content as in the last cycle)
# Source
#IS3G30A Talk to others about your views on political or social issues
#IS3G30B Contact an <elected representative>
#IS3G30C Take part in a peaceful march or rally
#IS3G30D Collect signatures for a petition
#IS3G30E Contribute to an online discussion forum about social or political issues
#IS3G30F Organize an online group to take a stance on a controversial political or social issue
#IS3G30G Participate in an online campaign

# Variable Name: S_ILLACT_rec 
# Description: Students' expected participation in illegal protest activities
# Procedure: IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation: Higher values indicating higher levels of expected engagement
# Trend Status: Not equated to ICCS 2009 given changes in stem and wording, new scale for ICCS 2016 (with similar content as in the last cycle)
# Source 
#IS3G30I Spray-paint protest slogans on walls
#IS3G30J Stage a protest by blocking traffic
#IS3G30K Occupy public buildings as a sign of protest

# Variable Name: S_ELECPART_rec 
# Description: Students' expected electoral participation
# Procedure: IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation: Higher values indicating higher levels of expected engagement
# Trend Status: Same scale as in ICCS 2009
# Source 
#IS3G31A Vote in <local elections>
#IS3G31B Vote in <national elections>
#IS3G31C Get information about candidates before voting in an election

##################################
#### Variables independientes ####
##################################

# Variable Name L_DISLAW_rec 
# Description Students' endorsement of disobedience to the law
# Procedure IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation Higher values indicating higher levels of endorsement of disobedience to the law
# Trend Status Same scale as in ICCS 2009
# Pregunta: ¿En qué medida está de acuerdo o en desacuerdo con las siguientes declaraciones sobre situaciones en las que se desobedece la ley?
# Se puede desobedecer una ley ...
# Source 
#LS3G05A When it is the only alternative left for achieving important objectives.
#LS3G05B When it is the only way one has to help one's family.
#LS3G05C When others who disobeyed it were not punished.
#LS3G05D When others do it.
#LS3G05E When one distrusts the enacting body.
#LS3G05F When one is sure nobody will realize.
#LS3G05H When nobody gets hurt.
#LS3G05I When it is not done with bad intentions. 
#LS3G05J When one can obtain economic benefits.

# Variable Name L_ATTVIOL_rec 
# Description Students' endorsement of the use of violence
# Procedure IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation Higher values indicating higher levels of endorsement toward violence
# Trend Status Same scale as in ICCS 2009 with additional items
# Source 
#LS3G04E He who does me harm will have to pay for it. 
#LS3G04F Watching fights between classmates is fun.
#LS3G04G If you can’t succeed by doing good things, <try> the bad ones.
#LS3G04H You have to fight so people do not think you are a coward.
#LS3G04I Revenge is sweet. (no se repite)
#LS3G04J Aggression serves to achieve what one wants. (no se repite)

# Variable Name S_CITEFF_rec 
# Description	 Students' sense of citizenship self-efficacy
# Procedure IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation	 Higher values indicating higherlevels of confidence
# Trend Status Same scale as in ICCS 2009
# Source
#IS3G29A Discuss a newspaper article about a conflict between countries
#IS3G29B Argue your point of view about a controversial political or social issue
#IS3G29C Stand as a candidate in a <school election>
#IS3G29D Organize a group of students in order to achieve changes at school
#IS3G29E Follow a television debate about a controversial issue
#IS3G29F Write a letter or email to a newspaper giving your view on a current issue
#IS3G29G Speak in front of your class about a social or political issue

# IS3G10A
# How interested are you and your parent(s) in political and social issues?
# Very interested (1) / Quite interested (2) / Not very interested (3) / Not interested at all (4)

# Variable Name S_SCHPART_rec 
# Description Students' participation at school
# Procedure IRT WLE scores with mean of 10 and standard deviation of 2 within each participating country
# Interpretation Higher values indicating higher levels of participation 
# Trend Status New scale for ICCS 2016
# Source 
#IS3G16A Active participation in an organized debate
#IS3G16B Voting for <class representative> or <school parliament>
#IS3G16C Taking part in decision-making about how the school is run
#IS3G16D Taking part in discussions at a <student assembly>
```

# Modelos de regresión multinivel: 2016
```{r, include=FALSE}
pacman::p_load(summarytools,haven,sjPlot,dplyr,lme4,haven,texreg,knitr,kableExtra,bda,lmerTest)

coef_names <- c(
          "Intercepto",
          "ISCED level 4, 5A, 5B or 6 (Ref. Level 3 or less)",
          "More than 100 books (Ref. 0-100 books)",
          "Attitudes towards disobeying the law",
          "Attitudes towards the use of violence",
          "Citizenship self-efficacy",
          "Civic participation at school (student)",
          "Civic participation at school (school)",
          "Civic knowledge"
          )

#omit_coef <- "(PV1CIV)"
#footnote<- "\\item %stars. \\item Todos los modelos son controlados por la región de residencia (p>0.05), la dependencia administrativa de la escuela (p>0.05) y el nivel de conocimiento cívico del estudiante ($p$<0.05)"
scale_box <- 0.825
```

## Participación política en actividades legales

### Chile
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_chl)
reg2 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_chl)
reg3 <- lmer(S_LEGACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_chl)
reg4 <- lmer(S_LEGACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_chl)
reg5 <- lmer(S_LEGACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_chl)
reg6 <- lmer(S_LEGACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_chl)
reg7 <- lmer(S_LEGACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_chl)
reg8 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_chl)

caption <- "Students' expected participation in future legal protest (Chile 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Colombia
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_col)
reg2 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_col)
reg3 <- lmer(S_LEGACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_col)
reg4 <- lmer(S_LEGACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_col)
reg5 <- lmer(S_LEGACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_col)
reg6 <- lmer(S_LEGACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_col)
reg7 <- lmer(S_LEGACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_col)
reg8 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_col)

caption <- "Students' expected participation in future legal protest (Colombia 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### República Dominicana
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_dom)
reg2 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_dom)
reg3 <- lmer(S_LEGACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_dom)
reg4 <- lmer(S_LEGACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_dom)
reg5 <- lmer(S_LEGACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_dom)
reg6 <- lmer(S_LEGACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_dom)
reg7 <- lmer(S_LEGACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_dom)
reg8 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_dom)

caption <- "Students' expected participation in future legal protest (Dominican Republic 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### México
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_mex)
reg2 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_mex)
reg3 <- lmer(S_LEGACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_mex)
reg4 <- lmer(S_LEGACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_mex)
reg5 <- lmer(S_LEGACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_mex)
reg6 <- lmer(S_LEGACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_mex)
reg7 <- lmer(S_LEGACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_mex)
reg8 <- lmer(S_LEGACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_mex)

caption <- "Students' expected participation in future legal protest (Mexico 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Todos los países
```{r, echo=FALSE, results='asis'}
data2016 <- rbind(data2016_chl,data2016_col,data2016_dom,data2016_mex)
data2016$IDSCHOOL2<- as.numeric(data2016$IDCNTRY*100000 + data2016$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2016$IDCNTRY2 <- ifelse((data2016$IDCNTRY==152), 1, # Chile
                   ifelse((data2016$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2016$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2016$IDCNTRY==484), 4, NA)))) # Mexico

reg1 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + (1 | IDSCHOOL2), data=data2016)
reg2 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + (1 | IDSCHOOL2), data=data2016)
reg3 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HOMLIT2) + (1 | IDSCHOOL2), data=data2016)
reg4 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + L_DISLAW_rec + (1 | IDSCHOOL2), data=data2016)
reg5 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + L_ATTVIOL_rec + (1 | IDSCHOOL2), data=data2016)
reg6 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + S_CITEFF_rec + (1 | IDSCHOOL2), data=data2016)
reg7 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL2), data=data2016)
reg8 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + PV1CIV + (1 | IDSCHOOL2), data=data2016)
reg9 <- lmer(S_LEGACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV+ (1 | IDSCHOOL2), data=data2016)

caption <- "Students' expected participation in future legal protest (2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8,reg9),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico", coef_names),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

## Participación política en actividades ilegales

### Chile
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_chl)
reg2 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_chl)
reg3 <- lmer(S_ILLACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_chl)
reg4 <- lmer(S_ILLACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_chl)
reg5 <- lmer(S_ILLACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_chl)
reg6 <- lmer(S_ILLACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_chl)
reg7 <- lmer(S_ILLACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_chl)
reg8 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_chl)

caption <- "Students' expected participation in future illegal protest (Chile 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Colombia
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_col)
reg2 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_col)
reg3 <- lmer(S_ILLACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_col)
reg4 <- lmer(S_ILLACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_col)
reg5 <- lmer(S_ILLACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_col)
reg6 <- lmer(S_ILLACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_col)
reg7 <- lmer(S_ILLACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_col)
reg8 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_col)

caption <- "Students' expected participation in future illegal protest (Colombia 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### República Dominicana
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_dom)
reg2 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_dom)
reg3 <- lmer(S_ILLACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_dom)
reg4 <- lmer(S_ILLACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_dom)
reg5 <- lmer(S_ILLACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_dom)
reg6 <- lmer(S_ILLACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_dom)
reg7 <- lmer(S_ILLACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_dom)
reg8 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_dom)

caption <- "Students' expected participation in future illegal protest (Dominican Republic 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### México
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_mex)
reg2 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_mex)
reg3 <- lmer(S_ILLACT_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_mex)
reg4 <- lmer(S_ILLACT_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_mex)
reg5 <- lmer(S_ILLACT_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_mex)
reg6 <- lmer(S_ILLACT_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_mex)
reg7 <- lmer(S_ILLACT_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_mex)
reg8 <- lmer(S_ILLACT_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_mex)

caption <- "Students' expected participation in future illegal protest (Mexico 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Todos los países
```{r, echo=FALSE, results='asis'}
data2016 <- rbind(data2016_chl,data2016_col,data2016_dom,data2016_mex)
data2016$IDSCHOOL2<- as.numeric(data2016$IDCNTRY*100000 + data2016$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2016$IDCNTRY2 <- ifelse((data2016$IDCNTRY==152), 1, # Chile
                   ifelse((data2016$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2016$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2016$IDCNTRY==484), 4, NA)))) # Mexico

reg1 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + (1 | IDSCHOOL2), data=data2016)
reg2 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + (1 | IDSCHOOL2), data=data2016)
reg3 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HOMLIT2) + (1 | IDSCHOOL2), data=data2016)
reg4 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + L_DISLAW_rec + (1 | IDSCHOOL2), data=data2016)
reg5 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + L_ATTVIOL_rec + (1 | IDSCHOOL2), data=data2016)
reg6 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + S_CITEFF_rec + (1 | IDSCHOOL2), data=data2016)
reg7 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL2), data=data2016)
reg8 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + PV1CIV + (1 | IDSCHOOL2), data=data2016)
reg9 <- lmer(S_ILLACT_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2016)

caption <- "Students' expected participation in future illegal protest (2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8,reg9),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c("Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico",coef_names),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

## Participación política formal

### Chile
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_chl)
reg2 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_chl)
reg3 <- lmer(S_ELECPART_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_chl)
reg4 <- lmer(S_ELECPART_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_chl)
reg5 <- lmer(S_ELECPART_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_chl)
reg6 <- lmer(S_ELECPART_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_chl)
reg7 <- lmer(S_ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_chl)
reg8 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_chl)

caption <- "Students' expected adult electoral participation (Chile 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Colombia
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_col)
reg2 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_col)
reg3 <- lmer(S_ELECPART_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_col)
reg4 <- lmer(S_ELECPART_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_col)
reg5 <- lmer(S_ELECPART_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_col)
reg6 <- lmer(S_ELECPART_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_col)
reg7 <- lmer(S_ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_col)
reg8 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_col)

caption <- "Students' expected adult electoral participation (Colombia 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### República Dominicana
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_dom)
reg2 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_dom)
reg3 <- lmer(S_ELECPART_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_dom)
reg4 <- lmer(S_ELECPART_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_dom)
reg5 <- lmer(S_ELECPART_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_dom)
reg6 <- lmer(S_ELECPART_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_dom)
reg7 <- lmer(S_ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_dom)
reg8 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_dom)

caption <- "Students' expected adult electoral participation (Dominican Republic 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### México
```{r, echo=FALSE, results='asis'}
reg1 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + (1 | IDSCHOOL), data=data2016_mex)
reg2 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HOMLIT2) + (1 | IDSCHOOL), data=data2016_mex)
reg3 <- lmer(S_ELECPART_rec ~ 1 + L_DISLAW_rec + (1 | IDSCHOOL), data=data2016_mex)
reg4 <- lmer(S_ELECPART_rec ~ 1 + L_ATTVIOL_rec + (1 | IDSCHOOL), data=data2016_mex)
reg5 <- lmer(S_ELECPART_rec ~ 1 + S_CITEFF_rec + (1 | IDSCHOOL), data=data2016_mex)
reg6 <- lmer(S_ELECPART_rec ~ 1 + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL), data=data2016_mex)
reg7 <- lmer(S_ELECPART_rec ~ 1 + PV1CIV + (1 | IDSCHOOL), data=data2016_mex)
reg8 <- lmer(S_ELECPART_rec ~ 1 + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL), data=data2016_mex)

caption <- "Students' expected adult electoral participation (Mexico 2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = coef_names,
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage

### Todos los países
```{r, echo=FALSE, results='asis'}
data2016 <- rbind(data2016_chl,data2016_col,data2016_dom,data2016_mex)
data2016$IDSCHOOL2<- as.numeric(data2016$IDCNTRY*100000 + data2016$IDSCHOOL) # se genera ID único por colegio (se repetían los mismos códigos entre países)

data2016$IDCNTRY2 <- ifelse((data2016$IDCNTRY==152), 1, # Chile
                   ifelse((data2016$IDCNTRY==170), 2, # Colombia                               
                          ifelse((data2016$IDCNTRY==214), 3, # Republica Dominicana
                                 ifelse((data2016$IDCNTRY==484), 4, NA)))) # Mexico

reg1 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + (1 | IDSCHOOL2), data=data2016)
reg2 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + (1 | IDSCHOOL2), data=data2016)
reg3 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(S_HOMLIT2) + (1 | IDSCHOOL2), data=data2016)
reg4 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + L_DISLAW_rec + (1 | IDSCHOOL2), data=data2016)
reg5 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + L_ATTVIOL_rec + (1 | IDSCHOOL2), data=data2016)
reg6 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + S_CITEFF_rec + (1 | IDSCHOOL2), data=data2016)
reg7 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + S_SCHPART_rec + mean_op_esc + (1 | IDSCHOOL2), data=data2016)
reg8 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + PV1CIV + (1 | IDSCHOOL2), data=data2016)
reg9 <- lmer(S_ELECPART_rec ~ 1 + factor(IDCNTRY2) + factor(S_HISCED2) + factor(S_HOMLIT2) + L_DISLAW_rec + L_ATTVIOL_rec + S_CITEFF_rec + S_SCHPART_rec + mean_op_esc + PV1CIV + (1 | IDSCHOOL2), data=data2016)

caption <- "Students' expected adult electoral participation (2016)"
knitreg(list(reg1,reg2,reg3,reg4,reg5,reg6,reg7,reg8,reg9),
        #custom.model.names = c("Modelo 1",  "Modelo 2",  "Modelo 3",  "Modelo 4",  
         #                      "Modelo 5",  "Modelo 6",  "Modelo 7"),
        #custom.note = footnote,
        threeparttable = TRUE,
        #omit.coef = omit_coef, 
        custom.coef.names = c(coef_names, 
                              "Colombia (Ref. Chile)",
                              "Dominican Republic",
                              "Mexico"),
       scalebox = 0.75,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
\newpage
